Supplement to Automatic Matching of Bullet Lands

### 2016-01-17 imaging-supplement.Rnw
Disable messages in the supplement

\newpage
\section{Signature intensities}\label{supp:bulletbottom}
<<setup-signatures, echo=FALSE>>=
library(x3pr)
library(x3prplus)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(zoo)

>>>>

\newpage
\section{Signature intensities}\label{supp:bulletbottom}
<<setup-signatures, echo=FALSE, message=FALSE>>=
library(x3pr)
library(x3prplus)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(zoo)
